---
title: "Homework_3_Tobie_Irvine"
author: "Tobie Irvine"
date: "September 26, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rgdal)
library(leaflet)
library(leaflet.extras)

library(dplyr)
library(readxl)
library(stringr)

```

## Homework 3 Description
Each map will include: 

.	A Basemap
.	One map with a layer of points
  o	Students may use either circles or markers
.	One map with a layer of lines
.	One map with a layer of polygons
.	One of the maps must contain a variable which changes of the color of the elements or the marker with an accompanying legend
.	One map must contain a functioning layersControl() 


## Get Spatial Data from online

```{r }
shape.data.load <- readOGR("file_name.shp", layer = "file_that_contains_shape_file", GDAL1_integer64_policy = TRUE)
#I have no idea what third argument does
```
## Using data from table and merging with spatial data
```{r }
pratical.data <- read_excel() %>% mutate(foreign.key = str_pad(foreign.key, 4, pad = "0"))
#mutate necessary in case you need to modify column that you will use to join shape # file and data file. foreign.key is name of column of you need to modify

#pick only rows that match practical datas foreign key values
shape.data.2 <- shape.data.load[shape.data.load$GEOID %in% practical.data$foreign.key]

#merge practical.data and shape.data.2 to get file used to create base map and 
# assign to data element of shape.data.2; MAKE SURE SORT IS FALSE

shape.2.data@data <- merge(shape.data.2, practical.data, sort = FALSE, by.x = "GEOID", by.y = "foreign.key")

```
A Basemap
```{r }
#Pick different map. Esri World Imagery is downloaded from website: add no wrap
leaflet() %>%
  addProviderTiles(providers$Esri.WorldImagery, options = providerTileOptions(noWrap = TRUE))

```
One map with a layer of points
```{r }

```
One map with a layer of lines
```{r }

```
One map with a layer of polygons
```{r }

```
One of the maps must contain a variable which changes of the color of the elements or the marker with an accompanying legend
```{r}

```
One map must contain a functioning layersControl()
```{r }

```


