---
title: "Homework_3_Tobie_Irvine"
author: "Tobie Irvine"
date: "September 26, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rgdal)
library(leaflet)
library(leaflet.extras)

library(dplyr)
library(readxl)
library(stringr)

```

## Homework 3 Description
Each map will include (3 maps): 

.	A Basemap
.1) 	One map with a layer of points
   o	Students may use either circles or markers
.2)	One map with a layer of lines
.3)	One map with a layer of polygons
Layers
.	One of the maps must contain a variable which changes of the color of the elements or the marker with an accompanying legend
.	One map must contain a functioning layersControl() 


## Get Spatial Data from online

```{r }
#, 
shape.data.load <- readOGR("./Pittsburgh_Parks", layer = "Pittsburgh_Parks")

#I have no idea what third argument does
# Last argument (GDAL_integer64_policy = TRUE) results in error: INTEGER() can only #be applied to a 'integer', not a 'double'

```
## Using data from table and merging with spatial data
```{r }
practical.data <- read.csv("Pittsburgh_Parks_1.csv") 
#%>% #mutate(objectid = #str_pad(objectid, 6 , pad = "0"))
#mutate necessary in case you need to modify column that you will use to join #shape # file and data file. foreign.key is name of column of you need to modify

#pick only rows that match practical datas foreign key values: objectid or #globalid
shape.data.2 <- shape.data.load[shape.data.load$GlobalID_2 %in% practical.data$GlobalID_2,]

#merge practical.data and shape.data.2 to get file used to create base map and 
# assign to data element of shape.data.2; MAKE SURE SORT IS FALSE

shape.data.2@data <- merge(shape.data.2@data, practical.data, sort = FALSE, by.x = "GlobalID_2", by.y = "GlobalID_2")

```
##A Basemap with polygons and the ability to pick different layers
```{r }
#Pick color palette
pal <- colorFactor(
  palette = "Purples",
  levels =shape.data.2$final_cat.y)


leaflet(shape.data.2) %>% addProviderTiles("OpenStreetMap.BlackAndWhite", options = providerTileOptions(noWrap = TRUE)) %>%
addPolygons(stroke = FALSE, color = ~pal(final_cat.y)) %>%
   addLegend(position = "bottomright", pal = pal, values = shape.data.2$final_cat.y , title = "Parks in Pittsburgh")



```


## A basemap with a layer of lines
```{r }
#get map with latitude and longitude for csv or look for GEOjson file
pa.rails <- readOGR("PaRailLines2018_07.geojson")
leaflet(data = pa.rails) %>%
  #addProviderTiles("OpenStreetMap.Mapnik") %>% 
  addProviderTiles("OpenMapSurfer.Roads", options = providerTileOptions(noWrap = TRUE), group = "Default") %>%
  addProviderTiles("Esri.DeLorme", options = providerTileOptions(noWrap = TRUE), group = "Topographical") %>%
  addProviderTiles(providers$Esri.WorldImagery, options = providerTileOptions(noWrap = TRUE), group = "World") %>%
  # Layers Control
    addLayersControl(
      baseGroups = c("Default", "Topographical", "World"),
      overlayGroups = c("Railroads"),
      options = layersControlOptions(collapsed = FALSE)
    )  %>% addPolylines(color = "#63CBD4", popup = ~LINENAME)
 

```
## A basemap with points
```{r }
# point.map <- readOGR("Pittsburgh_Bridges.geojson")
# 
# 
# leaflet() %>%
#   addProviderTiles("OpenMapSurfer.Roads")# %>% 
  #addCircleMarkers(data = point.map, lat = ~Latitude, lng = ~Longitude)
dat311 <- read.csv("2018-07-city-of-london-street.csv")

leaflet(data = dat311) %>%
  addProviderTiles("OpenStreetMap.HOT") %>%
  addCircleMarkers(lng = ~Longitude, lat = ~Latitude, radius = 1.5)

#color = ~pal311(STATUS), clusterOptions = markerClusterOptions())

# %>%
#   addLegend(position = "topright" , pal = pal311, values = dat311$STATUS, title = "Status")

# 
# leaflet(data = potOver) %>%
#   addProviderTiles("OpenStreetMap.HOT") %>%
#   addAwesomeMarkers(lng = ~X, lat = ~Y, icon = ~icons[REQUEST_TYPE], popup = ~REQUEST_TYPE)
```

```{r }

```
One of the maps must contain a variable which changes of the color of the elements or the marker with an accompanying legend
```{r}

```
One map must contain a functioning layersControl()
```{r }

```


